\Sethpageshiftt{11mm}   
\Setvpageshiftt{13mm}   
\vspace{0mm}

\Abstr{Motion capture is traditionally performed with marker-based systems. However, unlike markerless technologies, these solutions are hardly compatible with on-field sports analysis. One of the most promising prospects lies at the intersection of machine learning for 2D pose estimation, computer vision for 3D reconstruction from multiple video sources, and biomechanics for constraining 3D coordinates to an anatomically consistent model. We proposed and released Pose2Sim, an open-source package striving to answer these needs in a user-friendly way. OpenPose 2D keypoint coordinates are robustly triangulated, and serve as input for a full-body OpenSim inverse kinematics procedure. Pose2Sim robustness has been evaluated, regarding people entering and exiting the field of view, degraded image quality, calibration errors, and low number of cameras. Its accuracy has also been assessed, and deemed sufficient for walking, running, and cycling analysis. In the context of a competition, using lightweight action cameras can be convenient. We tested such hardware on boxing sequences, and proposed post-calibration and post-synchronization procedures. Finally, capturing the equipment of the athlete along with them would be interesting. We explored the inverse kinematics of both a pilot and his bike in BMX race, with a custom DeepLabCut model, triangulated and mapped on a custom OpenSim skeletal model. This work brings out interesting perspectives for the analysis of sports movement.}


\Resume{La capture de mouvement est traditionnellement effectuée à l'aide de marqueurs réfléchissants. Cependant, au contraire des techniques sans marqueurs, ces méthodes ne conviennent pas à l'analyse contextuelle du sport. L'une des perspectives les plus prometteuses à ce sujet se situe à l'intersection de l'apprentissage machine pour l'estimation de pose 2D, de la vision par ordinateur pour la reconstruction 3D à partir de plusieurs sources vidéo, et de la biomécanique pour contraindre les coordonnées 3D à un modèle anatomiquement cohérent. Nous avons proposé et publié Pose2Sim, un package open-source et simple d'utilisation visant à répondre à ces besoins. Les détections 2D d'OpenPose sont triangulées de manière robuste, et transmises à OpenSim pour une cinématique inverse corps complet. La robustesse de Pose2Sim a été estimée, face à des personnes "parasites" entrant le champ de vision, à une qualité d'image dégradée, à des erreurs de calibration, et à un nombre de caméras réduit. Son exactitude a également été évaluée, et jugée satisfaisante pour l'analyse de la marche, de la course et du cyclisme. Dans un contexte de compétition, il peut être utile d'employer des caméras légères de type GoPro. Nous avons testé ce matériel sur des séquences de boxe, et proposé des procédures de post-calibration et de post-synchronisation. Enfin, capturer à la fois l'athlète et son équipement serait intéressant. Nous avons calculé la cinématique inverse d'un pilote de BMX avec son vélo, en entraînant un modèle DeepLabCut personnalisé, triangulé et appliqué sur un modèle squelettique OpenSim personnalisé. L'ensemble de ces résultats apporte des perspectives intéressantes pour l'analyse du mouvement sportif.} 


\Keywords{Markerless motion capture; Sports performance analysis; Kinematics; Computer vision; OpenPose; OpenSim; Python package}

\MakeUGthesePDC

